---
output:
  html_document: default
  pdf_document: default
---
```{r, include=FALSE}
library(tidyverse)
library(ggrepel)
library(scales)
```

```{r}
source("cleaning_pipeline.R")
```
We're going to add the peak number of concurrent players for each game to our dataset. From the previously selected games, we'll only keep those that have a value when merged with the peak dataset.
```{r}
scrapdb <- read_csv("./../scraping/steamdb_top_peaks_cleaned.csv") |>
  rename(c("all_time_peak" = "All-Time Peak","24h_peak" = "24h Peak", 
           "name" = "Name"))
```
```{r}
df_final <- merge(df_final, scrapdb |> select(-all_of("name")), by = "appid", all.x = TRUE) |>
  filter(!is.na(all_time_peak))
```

We want to study what determines a game's successful performance. To do this, instead of defining success ourselves, we'll let the data tell us by applying clustering techniques to performance data.

To do this, we'll determine which columns in our dataset provide information about the game's performance after its release.
```{r}
performance_cols <- c(
  "median_playtime_forever", "median_playtime_2weeks",
  "recommendations", "owners_avg", "total_positive",
  "total_reviews", "num_tag_association", "all_time_peak"
)
```

First of all, we know that clustering methods are quite sensitive to outliers. For this reason, we're going to study whether there are any outlier games by analyzing the selected variables. We'll start by looking at the variables that allow us to identify outliers generated by games where bots play to earn collectible cards that can then be sold. We're not interested in including these games in the success study because they will distort the analysis.
```{r, fig.height=7, fig.width=12, warning=FALSE, echo=FALSE}
cols_playtime <- performance_cols

# 1. Data Preparation and Outlier Detection
data_plot <- df_final |>
  select(name, all_of(cols_playtime)) |>
  pivot_longer(cols = all_of(cols_playtime), names_to = "metrica", values_to = "valor") |>
  filter(valor > 0) |>
  group_by(metrica) |>
  mutate(
    # Boxplot Calculations
    Q1 = quantile(valor, 0.25),
    Q3 = quantile(valor, 0.75),
    IQR = Q3 - Q1,
    upper_limit = Q3 + 1.5 * IQR,

    # Identify outliers
    is_outlier = valor > upper_limit
  ) |>
  arrange(metrica, desc(valor)) |>
  mutate(
    ranking_outlier = row_number(),
    # We only create a label if it's an outlier AND it's in the Top 10
    label_text = ifelse(is_outlier & ranking_outlier <= 10, name, NA)
  ) |>
  ungroup()

# 2. Graph Generation
ggplot(data_plot, aes(x = metrica, y = valor)) +
  geom_jitter(
    data = filter(data_plot, !is_outlier),
    color = "#b3cde0", alpha = 0.3, width = 0.2
  ) +
  geom_point(
    data = filter(data_plot, is_outlier),
    color = "#d9534f", alpha = 0.6, size = 1.5
  ) +
  geom_boxplot(fill = NA, color = "#2c3e50", outlier.shape = NA, width = 0.5) +
  geom_text_repel(
    aes(label = label_text),
    size = 3,
    color = "#c0392b",
    fontface = "bold",
    min.segment.length = 0,
    box.padding = 0.5,
    max.overlaps = Inf,
    nudge_x = 0.5,
    direction = "y"
  ) +
  facet_wrap(~metrica, scales = "free", ncol = 3) +
  theme_minimal() +
  labs(
    title = "Playtime Distribution: Top 10 Labeled Outliers",
    subtitle = "The red dots are outliers (according to the boxplot). Only the 10 most extreme ones are labeled for readability.",
    y = "",
    x = ""
  ) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(face = "bold", size = 11)
  )
```
This graph shows exorbitant values for both 'median_paytime_2weeks' and 'median_playtime_forever'. These are most likely farming games where bots play for human players (such as LoveKami, A Sky Full of Stars, Hatsune Miku VR NEKOPARA, etc.) to obtain trading cards and then sell them on the Steam market.

In the remaining boxplots, we can see that the games at the top are truly successful and famous, so we can't remove them. What we'll do is convert these variables to a logarithmic scale so the gap isn't so large and allows us to better differentiate between those that aren't as famous or haven't been as successful.

# Detect and fix outliers

So, let's focus on detecting and fixing the outliers we observed with the variables 'median_playtime_2weeks' and 'median_playtime_forever'. Instead of detecting and eliminating the outliers using a quantile or an invented threshold, we'll apply the k-means clustering method to separate these two distinct groups. Therefore, we'll use k=2.
```{r clustering, echo=FALSE}
library(dplyr)
library(ggplot2)

time_cols <- c("median_playtime_forever", "median_playtime_2weeks")

df_time_cluster <- df_final %>%
  select(all_of(time_cols))

# Scale
df_time_scaled <- df_time_cluster %>%
  mutate(across(everything(), scale))

# K=2 (Normal vs Anormal)
set.seed(8)
kmeans_time <- kmeans(df_time_scaled, centers = 2, nstart = 25)

df_final$cluster_time <- as.factor(kmeans_time$cluster)

resumen_limpieza <- df_final %>%
  group_by(cluster_time) %>%
  summarise(
    Total_Juegos = n(),
    Min_MedianPlaytimeF = min(median_playtime_forever, na.rm = T),
    Max_MedianPlaytimeF = max(median_playtime_forever, na.rm = T),
    Avg_MedianPlaytimeF = mean(median_playtime_forever, na.rm = T),
    Min_MedianPlaytime2W = min(median_playtime_2weeks, na.rm = T),
    Max_MedianPlaytime2W = max(median_playtime_2weeks, na.rm = T),
    Avg_MedianPlaytime2W = mean(median_playtime_2weeks, na.rm = T),
    Ejemplos = paste(head(name, 3), collapse = ", ")
  ) %>%
  arrange(desc(Avg_MedianPlaytimeF))

print(resumen_limpieza)
```
Here, with the maximums and averages of the elements of each of the clusters, we can see that there is a very large difference between groups.
```{r}
ggplot(df_final, aes(x = median_playtime_forever, y = median_playtime_2weeks, 
                     color = factor(cluster_time))) + # Convertimos a factor aquí
  geom_point(alpha = 0.5) +
  geom_text_repel(data = subset(df_final, cluster_time == 1), 
                  aes(label = name), show.legend = FALSE) +
  theme_minimal() +
  labs(
    title = "Bot detection by playtime",
    x = "Total playtime (median)",
    y = "Median playtime last 2 weeks",
    color = "Game type"
  ) +
  scale_color_manual(
    values = c("1" = "#E67E22", "2" = "#2E86C1"),
    labels = c("1" = "Abnormal", "2" = "Normal")
  )
```
At first glance, we can see that k-means has managed to separate the games into two groups: those with exorbitant variable values and those that appear to have more natural and human-like behavior. For this reason, we will only consider the games that belong to the "Normal" cluster.

```{r}
df_final <- df_final |> filter(cluster_time == 2)
```

Let's analyze the boxplots again:
```{r, fig.height=7, fig.width=12, warning=FALSE, echo=FALSE}
cols_playtime <- performance_cols

data_plot <- df_final |>
  select(name, all_of(cols_playtime)) |>
  pivot_longer(cols = all_of(cols_playtime), names_to = "metrica", values_to = "valor") |>
  filter(valor > 0) |>
  group_by(metrica) |>
  mutate(
    Q1 = quantile(valor, 0.25),
    Q3 = quantile(valor, 0.75),
    IQR = Q3 - Q1,
    upper_limit = Q3 + 1.5 * IQR,

    is_outlier = valor > upper_limit
  ) |>
  arrange(metrica, desc(valor)) |>
  mutate(
    ranking_outlier = row_number(),
    label_text = ifelse(is_outlier & ranking_outlier <= 10, name, NA)
  ) |>
  ungroup()

ggplot(data_plot, aes(x = metrica, y = valor)) +
  geom_jitter(
    data = filter(data_plot, !is_outlier),
    color = "#b3cde0", alpha = 0.3, width = 0.2
  ) +
  geom_point(
    data = filter(data_plot, is_outlier),
    color = "#d9534f", alpha = 0.6, size = 1.5
  ) +
  geom_boxplot(fill = NA, color = "#2c3e50", outlier.shape = NA, width = 0.5) +
  geom_text_repel(
    aes(label = label_text),
    size = 3,
    color = "#c0392b",
    fontface = "bold",
    min.segment.length = 0,
    box.padding = 0.5,
    max.overlaps = Inf,
    nudge_x = 0.5,
    direction = "y"
  ) +
  facet_wrap(~metrica, scales = "free", ncol = 2) +
  theme_minimal() +
  labs(
    title = "Playtime Distribution: Top 10 Labeled Outliers",
    subtitle = "The red dots are outliers (according to the boxplot). Only the 10 most extreme ones are labeled for readability.",
    y = "Time (Minutes - Log Scale)",
    x = ""
  ) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(face = "bold", size = 11)
  )
```
```{r, echo=FALSE}
ggplot(df_final, aes(x = median_playtime_forever, y = median_playtime_2weeks)) +
  geom_point(alpha = 0.5) +
  theme_minimal() +
  labs(
    title = "Distribution by playing time",
  )
```
With the previous plots we can already observe that the data may follow more normal behaviors but that there are still different groups.

# Transform variables to a logarithmic scale
Since most variables show a long-tailed distribution to the right, the most popular games distort the distances due to their large magnitude. Therefore, we will apply the logarithmic transformation to "compress" the range of the highest values and expand the low ones, facilitating a clearer differentiation between games of average success.

```{r}
new_log_cols <- paste0(performance_cols, "_log")


df_performance_log <- df_final %>%
  mutate(
    across(
      .cols = all_of(performance_cols),
      .fns = log1p,
      .names = "{.col}_log"
    )
  ) |>
  select(all_of(c("appid", "name", "days_since_release", new_log_cols)))
print(colnames(df_performance_log))
```
Once the logarithmic scale is done, let's see how the boxplots turned out:
```{r, fig.height=5, fig.width=8, warning=FALSE, echo=FALSE}
cols <- c("recommendations_log", "owners_avg_log", "total_positive_log",
          "total_reviews_log", "num_tag_association_log", 
          "median_playtime_forever_log", "median_playtime_2weeks_log", 
          "all_time_peak_log")

data_plot <- df_performance_log |>
  select(name, all_of(cols)) |>
  pivot_longer(cols = all_of(cols), names_to = "metrica", values_to = "valor") |>
  filter(valor > 0) |>
  group_by(metrica) |>
  mutate(
    Q1 = quantile(valor, 0.25),
    Q3 = quantile(valor, 0.75),
    IQR = Q3 - Q1,
    upper_limit = Q3 + 1.5 * IQR,
    is_outlier = valor > upper_limit
  ) |>
  arrange(metrica, desc(valor)) |>
  mutate(
    ranking_outlier = row_number(),
    label_text = ifelse(is_outlier & ranking_outlier <= 10, name, NA)
  ) |>
  ungroup()

ggplot(data_plot, aes(x = metrica, y = valor)) +
  geom_jitter(
    data = filter(data_plot, !is_outlier),
    color = "#b3cde0", alpha = 0.3, width = 0.2
  ) +
  geom_point(
    data = filter(data_plot, is_outlier),
    color = "#d9534f", alpha = 0.6, size = 1.5
  ) +
  geom_boxplot(fill = NA, color = "#2c3e50", outlier.shape = NA, width = 0.5) +
  facet_wrap(~metrica, scales = "free", ncol = 3) +
  theme_minimal() +
  labs(
    title = "Distribution of performance variables",
    y = "",
    x = ""
  ) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(face = "bold", size = 11)
  )
```
# Normalize cumulative variables by age
The next step we take is to convert the selected cumulative variables into variables that indicate speed, that is, to divide those cumulative variables by the launch time.
```{r}
df_performance <- df_performance_log |>
  mutate(
    recommendations_log_per_day = recommendations_log / days_since_release,
    owners_avg_log_per_day = owners_avg_log / days_since_release,
    total_positive_log_per_day = total_positive_log / days_since_release,
    total_reviews_log_per_day = total_reviews_log / days_since_release,
    num_tag_association_log_per_day = num_tag_association_log /days_since_release 
  ) |>
  select(appid, name, median_playtime_forever_log, median_playtime_2weeks_log, 
         recommendations_log_per_day, owners_avg_log_per_day, total_positive_log_per_day,
         total_reviews_log_per_day, num_tag_association_log_per_day, all_time_peak_log)
```

We have now been able to differentiate these two behaviors, selected the one we want to study, and generated new metrics to reduce seniority bias. We will now examine which of the selected 'performance' variables are correlated in order to eliminate or transform them, with the aim of reducing multicollinearity.
```{r, echo=FALSE, fig.width=10}
library(tidyverse)
library(corrplot)

cor_matrix <- cor(df_performance %>% select(-all_of(c("appid", "name"))))

corrplot(cor_matrix, 
         method = "color",
         type = "upper",
         order = "hclust",
         addCoef.col = "black",
         tl.col = "black",
         tl.srt = 45
)
```

Here we have two groups: one uncorrelated and the other with almost perfect correlation.

- The uncorrelated group relates to average playtime per user and peak player count. We will retain these variables, as they will help us measure retention, engagement, and the game's popularity at a given point.

- The almost perfectly correlated variables, in terms of growth rate, are a single dimension given the correlation. If a game's sales grow rapidly, its reviews will also increase. All of this is measured in terms of velocity (per day).

# PCA to eliminate multicollinearity

To eliminate multicollinearity without affecting the data by removing information, we will perform PCA on the columns 'recommendations_log_per_day', 'owners_avg_log_per_day', 'total_positive_log_per_day', 'total_reviews_log_per_day', and 'num_tag_association_log_per_day'.

```{r, echo=FALSE}
pca_data <- df_performance |> select(recommendations_log_per_day, 
                                     owners_avg_log_per_day, 
                                     total_positive_log_per_day, 
                                     total_reviews_log_per_day, 
                                     num_tag_association_log_per_day
                                    )
pca_result <- prcomp(pca_data, center = TRUE, scale = TRUE)

summary(pca_result)
```
These results show that a single component captures almost 98% of the total variance in the data, while the second component only contributes a 1.17% increase. Adding another component (PC2) would further complicate the analysis. Therefore, we will use only the first component (PC1), as it provides 97.8% of the variance and allows us to greatly simplify the explanation without losing much information.

Furthermore, according to Kaiser's criterion, which dictates that we use components with an eigenvalue greater than 1, we can discard all but the first component, since the second (PC2) has an eigenvalue of 0.2362.

Let's examine the composition of Principal Component 1 (PC1):
```{r, echo=FALSE}
pca_result$rotation
```
The five variables have positive and almost identical values, which tells us that PC1 is a metric that represents the overall logarithmic growth rate of a game.


# Variables we'll use for clustering and separating by popularity/success

We'll keep 4 variables:

- median_playtime_forever: Measures player retention.
- median_playtime_2weeks: Measures recent engagement.
- all_time_peak_log: Measures the maximum number of players a game has reached.
- PC1: Measures popularity/log growth rate per day.

We'll combine the columns and rename PC1 to growth_log_rate.
```{r}
pca_scores <- as.data.frame(pca_result$x)

df_pca_scores <- pca_scores |>
  select(PC1) |>
  rename(growth_log_rate = PC1)

df_base <- df_performance |>
  select(appid, name, median_playtime_forever_log, median_playtime_2weeks_log,
         all_time_peak_log)

df_performance <- cbind(df_base, df_pca_scores)

head(df_performance)
```
```{r, fig.width=10}
cor_matrix <- cor(df_performance %>% select(-all_of(c("appid", "name"))))


corrplot(cor_matrix, 
         method = "color", 
         type = "upper",        # Solo la mitad superior (la otra es espejo)
         order = "hclust",      # Agrupa las variables parecidas juntas
         addCoef.col = "black", # Muestra el número
         tl.col = "black",      # Color del texto
         tl.srt = 45,           # Rotación del texto
)
```
It's worth noting that from this point on, since the variables are now uncorrelated, we can use the Euclidean distance between games. If we had left the variables correlated, we would have had to use Mahalanobis, for example.

Let's visualize this in 3D for better understanding; we'll omit the all_time_peak_log from the plot.
```{r, echo=FALSE}
library(plotly)
plot_ly(df_performance, 
        x = ~median_playtime_forever_log, 
        y = ~median_playtime_2weeks_log, 
        z = ~growth_log_rate, 
        type = "scatter3d", 
        mode = "markers", 
        text = ~name, 
        hovertemplate = paste(
          "<b>Juego: %{text}</b><br>",
          "Playtime Forever (X): %{x:.2f} min<br>",
          "Playtime 2 Semanas (Y): %{y:.2f} min<br>",
          "Tasa Crecimiento (Z): %{z:.2f}<br>",
          "<extra></extra>"
        ),
        marker = list(size = 3, opacity = 0.5))
```


We prepared the data for clustering:
```{r}
cols_cluster <- c("median_playtime_forever_log", 
                  "median_playtime_2weeks_log", 
                  "growth_log_rate",
                  "all_time_peak_log")

df_scaled <- df_performance |>
  select(all_of(cols_cluster)) |>
  scale()

head(df_scaled)
```
We will perform the Hopkins test to see if the data tends to be clustered.
```{r}
library(factoextra)
library(clustertend)
set.seed(123)

datos_para_hopkins <- df_scaled[sample(nrow(df_scaled), 2000), ]

# Usamos n=1000 para reducir la carga computacional.
res_hopkins <- get_clust_tendency(datos_para_hopkins, n = 1000, graph = FALSE)

print(res_hopkins$hopkins_stat)
```
This value of 0.9322522 indicates that the data do tend to cluster and do not follow a uniform distribution.

## We are going to perform DBCSCAN with the 4 columns we have.

Let's try several eps values to see the results we get:
```{r}
library(dbscan)

valores_eps <- c(0.35, 0.4, 0.45, 0.5)
minPts_value <- 10

for(e in valores_eps){
  set.seed(123)
  db_test <- dbscan(df_scaled, eps = e, minPts = minPts_value)
  
  cat("\n--------------------------------\n")
  cat("TEST with eps =", e, "| minPts =", minPts_value, "\n")
  print(table(db_test$cluster))
}
```
We'll keep eps=0.35 and minPts=10 for example and let's visualize it.
```{r}
set.seed(123)
db_final_dbscan <- dbscan(df_scaled, eps = 0.35, minPts = 10)

df_performance_dbscan <- df_performance
df_performance_dbscan$cluster_dbscan <- as.factor(db_final_dbscan$cluster)
```

```{r}
perfil_clusters <- df_performance_dbscan %>%
  group_by(cluster_dbscan) %>%
  summarise(
    Count = n(),
    Avg_Playtime_Forever_Log = mean(median_playtime_forever_log, na.rm = TRUE),
    Avg_Playtime_2Weeks_Log = mean(median_playtime_2weeks_log, na.rm = TRUE),
    Avg_Peack_Log = mean(all_time_peak_log, na.rm = TRUE),
    Avg_Growth_Rate = mean(growth_log_rate, na.rm = TRUE),
    Examples = paste(head(name, 2), collapse = ", ") 
  ) %>%
  arrange(desc(Avg_Growth_Rate))

print(perfil_clusters)
```

```{r}
df_long <- df_performance_dbscan %>%
  select(cluster_dbscan, median_playtime_forever_log, median_playtime_2weeks_log, growth_log_rate, all_time_peak_log) %>%
  pivot_longer(cols = -cluster_dbscan, names_to = "Variable", values_to = "Valor")

# Boxplot comparativo
ggplot(df_long, aes(x = cluster_dbscan, y = Valor, fill = cluster_dbscan)) +
  geom_boxplot(outlier.alpha = 0.3) +
  facet_wrap(~Variable, scales = "free_y", ncol = 1) +
  theme_minimal() +
  labs(title = "Comparison of profiles by cluster",
       subtitle = "Cluster 0 = outliers",
       x = "Cluster",
       y = "Value") +
  scale_fill_brewer(palette = "Set2")
```
```{r}
library(plotly)

df_performance_dbscan$cluster_dbscan <- as.factor(df_performance_dbscan$cluster_dbscan)

mis_colores <- c("0" = "#FF0000", # Red for the Outliers
                 "1" = "#E0E0E0",
                 "2" = "#00CC00",
                 "3" = "#FF9900",
                 "4" = "#9900CC",
                 "5" = "#685669",
                 "6" = "#0099CC")


plot_ly(df_performance_dbscan, 
        x = ~median_playtime_forever_log, 
        y = ~median_playtime_2weeks_log, 
        z = ~growth_log_rate, 
        color = ~cluster_dbscan, 
        colors = mis_colores,
        type = "scatter3d", 
        mode = "markers", 
        text = ~name, 
        hovertemplate = paste(
          "<b>%{text}</b><br>",
          "Cluster: %{marker.color}<br>",
          "Forever (Log): %{x:.2f}<br>", 
          "2Weeks (Log): %{y:.2f}<br>", 
          "Growth: %{z:.2f}<br>",
          "<extra></extra>"
        ),
        marker = list(
          size = 3, 
          opacity = 0.7,
          line = list(width = 0)
        )
) %>%
  layout(
    title = "Steam Success Clustering (DBSCAN) eps=0.35 minpts=10",
    scene = list(
      xaxis = list(title = 'Total Retention (Forever)'),
      yaxis = list(title = 'Recent Engagement (2 Weeks)'),
      zaxis = list(title = 'Growth Rate')
    ),
    legend = list(title = list(text = 'Cluster'))
  )
```
After testing with various eps and minpts values, we found nothing relevant; most of the games played in the last two weeks are noise, and those that haven't been played are all very clustered together.

Let's try separating the data into two groups: those who have played in the last two weeks and those who haven't played in this period.

```{r}
df_performance_splited <- df_performance %>%
  mutate(status = ifelse(median_playtime_2weeks_log > 0, "Active", "Dormant"))

table(df_performance_splited$status)
```
We will conduct a study of only active games:
```{r}
df_performance_only_active <- df_performance_splited %>% filter(status == "Active") %>% select(-status)
df_performance_active <- df_performance_splited %>% filter(status == "Active")

# Seleccionamos las columnas para clusterizar (ya escaladas)
# Nota: Es mejor re-escalar solo este subconjunto para que la media se ajuste a ELLOS.
cols_cluster <- c("median_playtime_forever_log", 
                  "median_playtime_2weeks_log", 
                  "growth_log_rate", 
                  "all_time_peak_log")

df_active_scaled <- df_performance_active %>%
  select(all_of(cols_cluster)) %>%
  scale()
```

Let's see if this set of games tends to form groups like the complete set did:
```{r}
library(factoextra)
library(clustertend)
set.seed(123)

# Usamos n=500 para reducir la carga computacional.
res_hopkins <- get_clust_tendency(df_active_scaled, n = 500, graph = FALSE)

print(res_hopkins$hopkins_stat)
```
This Hopkins test value of 0.8217709 is a good value and indicates that it tends to form groups.

# Hierarchical clustering
Since these active games have different densities, we will try using a hierarchical method instead of DBSCAN, which is affected by varying densities.
```{r}
library(tidyverse)
library(factoextra)

cols_cluster <- c("median_playtime_forever_log", 
                  "median_playtime_2weeks_log", 
                  "growth_log_rate", 
                  "all_time_peak_log")

df_scaled_hc <- df_performance_only_active %>%
  select(all_of(cols_cluster)) %>%
  scale()

# We use Euclidean distance because the data is uncorrelated
dist_matrix <- dist(df_scaled_hc, method = "euclidean")

# We will use average linkage
hc_average <- hclust(dist_matrix, method = "average")
```

With the dendrogram we obtain, it is difficult to select a K. An optimal value is not visible at first glance.
```{r}
fviz_dend(hc_average, 
          k = 4,
          cex = 0.5,
          k_colors = "jco",
          color_labels_by_k = TRUE, 
          rect = TRUE,
          main = "Success Dendrogram (Average Linkage) K=4"
)
```
We will select K=4 but we see that we will obtain one very large group and others of smaller ones.
```{r}
df_performance_active_hc <- df_performance_only_active

grupos_hc <- cutree(hc_average, k = 4)

df_performance_active_hc$cluster_jerarquico <- as.factor(grupos_hc)

table(df_performance_active_hc$cluster_jerarquico)
```
```{r}
df_long_hc <- df_performance_active_hc %>%
  select(cluster_jerarquico, all_of(cols_cluster)) %>%
  pivot_longer(cols = -cluster_jerarquico, names_to = "Variable", values_to = "Valor")

ggplot(df_long_hc, aes(x = cluster_jerarquico, y = Valor, fill = cluster_jerarquico)) +
  geom_boxplot(outlier.size = 0.5, alpha = 0.7) +
  facet_wrap(~Variable, scales = "free_y") +
  theme_minimal() +
  labs(
    title = "Profiles defined by Hierarchical (Average Linkage)",,
    x = "Cluster",
    y = "Value (Log)"
  )
```
```{r}
library(plotly)

mis_colores <- c("1" = "grey",
                 "2" = "#00CC00",
                 "3" = "#FF9900",
                 "4" = "#9900CC",
                 "5" = "#685669",
                 "6" = "#0099CC")


plot_ly(df_performance_active_hc, 
        x = ~median_playtime_forever_log, 
        y = ~median_playtime_2weeks_log, 
        z = ~growth_log_rate, 
        color = ~cluster_jerarquico, 
        colors = mis_colores,
        type = "scatter3d", 
        mode = "markers", 
        text = ~name, 
        hovertemplate = paste(
          "<b>%{text}</b><br>",
          "Cluster: %{marker.color}<br>",
          "Forever (Log): %{x:.2f}<br>", 
          "2Weeks (Log): %{y:.2f}<br>", 
          "Growth: %{z:.2f}<br>",
          "<extra></extra>"
        ),
        marker = list(
          size = 3, 
          opacity = 0.7,
          line = list(width = 0)
        )
) %>%
  layout(
    title = "Success Clustering on Steam (Hierarchical)",
    scene = list(
      xaxis = list(title = 'Total Retention (Forever)'),
      yaxis = list(title = 'Recent Engagement (2 Weeks)'),
      zaxis = list(title = 'Growth Rate')
    ),
    legend = list(title = list(text = 'Cluster'))
  )
```

Very small groups form, and we don't think they can give us much information.

For this reason, we consider this a first attempt and proceed to make a second one.
